Novel lattice Boltzmann method for simulation of strongly shear thinning viscoelastic fluids

### 2024-03-08 NovelLBM.tex
small corrections

yields the first normal stress difference $N_1$ as follows. The second normal stress difference is proportional to $\xi$ and therefore $0$.

@@

@@

We start with the Cauchy momentum equation (neglecting gravity), which reads as follows.

@@

		0 &= 2\epsilon\lambda^2\dot{\gamma}^2\left[\partial_xp\frac{r}{2^j\dot{\gamma}\eta_\text{p}} - \frac{\eta_\text{s}}{\eta_\text{p}}\right]^2 + \ln\left(\partial_xp\frac{r}{2^j\dot{\gamma}\eta_\text{p}}-\frac{\eta_\text{s}}{\eta_\text{p}}\right) \\

>>>>

yields the first normal stress difference $N_1$ as follows.

@@

The second normal stress difference, which is defined as follows, is zero on account of the components in the equation being zero.
	N_2 = \begin{cases}
		\sigma_{yy} - \sigma_{zz} = \tau_{yy} - \tau_{zz},\quad\text{in 2D} \\
		\sigma_{rr} - \sigma_{\varphi\varphi} = \tau_{rr} - \tau_{\varphi\varphi},\quad\text{in 3D}
	\end{cases} = 0
\RK{zz Komponente in 2D ist ein bischen fragwürdig... Da beißt mich jetzt, dass ich mit 2D eigentlich channel flow meine. Sollte man bei der geometrie oben evtl. erwähnen. $N_2$ proportional zu $\xi$ stimmt übrigens. Aufgrund von $\sigma_{ii} = \tau_{ii}$ kann man für $N_1$ und $N_2$ nämlich die Lösungen für $\eta_\text{s} = 0$ verwenden (siehe ferras\cite{ferras2019})}

@@

We start with the Navier-Stokes equation (neglecting gravity), which reads as follows.

@@
